---
title: "Bitcoin Analysis"
output:
  html_document: 
    toc: TRUE
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(plotly)
library(quantmod)
library(qwraps2)
library(knitr)
library(dplyr)


# Preliminary Functions
# 
# Function for Determining Capital Growth over time
KapitalGrowth <- function(x, y){
  m <- length(y)
  y <- y/100
  k <- vector()
  g <- vector()
  k[1] <- x
  for(i in 2:m){
    g[i]<- k[i-1]*y[i]
    k[i]<- k[i-1] + g[i]
  }
  return(k)
}

# Function for Determining Returns of a Given Stock or Index
Returns_p <- function(x) {
  Returns <- vector()
  for(i in 2:length(x)){
    Returns[i]  <- ((x[i] - x[i-1])/x[i-1])*100
  }
  return(Returns)
}

LagReturns1 <- function(x) {
  LagReturns1 <- vector()
  for(i in 2:length(x)){
    LagReturns1[i] <- (x[i-1])
  }
  return(LagReturns1)
}

# Function for Determing the Value at Risk Assuming Normal Distribution
NDVaR <- function(x){
  MU <- mean(x, na.rm = T)
  SD <- sd(x, na.rm = T)
  NDV <- MU + qnorm(.05)*SD
  return(NDV)
}

# Function for Determing the Value at Risk Assuming Non-Normal Distribution
NON_NDVaR <- function(x){
  temp0 <- na.omit(x)
  o.x <- sort(temp0,decreasing = F)
  i <- .05*length(o.x)
  i.r <- round(i)
  d <- abs(i.r-1- i)
  NNVaR <- o.x[i.r-1] + d*(abs(o.x[i.r-1]-o.x[i.r]))
  return(NNVaR)
}

LagReturns1 <- function(x) {
  LagReturns1 <- vector()
  for(i in 2:length(x)){
    LagReturns1[i] <- (x[i-1])
  }
  return(LagReturns1)
}

tex2markdown <- function(texstring) {
  writeLines(text = texstring,
             con = myfile <- tempfile(fileext = ".tex"))
  texfile <- pandoc(input = myfile, format = "html")
  cat(readLines(texfile), sep = "\n")
  unlink(c(myfile, texfile))
}

BTC <- read.csv("C:/Users/jeanp/OneDrive/Documents/GitHub/BTC.csv")


BTC$Returns <- Returns_p(BTC$Adj.Close)
BTC$lReturns <- Returns_p(log(BTC$Adj.Close))
DeterministicPrice <- function(x, y, w){
  LinearDeterministic <- rep(NA, w)
  LinearDeterministic[1] <- y
    for(i in 2:w) {
    LinearDeterministic[i] <- LinearDeterministic[i-1]*x + LinearDeterministic[i-1]
    }
  return(LinearDeterministic)
}

BTC$LinearDeterministic <- DeterministicPrice(mean(BTC$Returns/100, na.rm = TRUE), 457.334, nrow(BTC))
LinearDeterministic <- DeterministicPrice(mean(BTC$Returns/100, na.rm = TRUE), 457.334, nrow(BTC))

y <- BTC$Returns
x <- 5000
mean(BTC$Returns, na.rm = TRUE)
sum(BTC$Returns, na.rm = TRUE)
min(BTC$Returns, na.rm = TRUE)
max(BTC$Returns, na.rm = TRUE)
median(BTC$Returns, na.rm = TRUE)
sd(BTC$Returns, na.rm = TRUE)
var(BTC$Returns, na.rm = TRUE)
NDVaR(BTC$Returns)
NON_NDVaR(BTC$Returns)

options(qwraps2_markup = "markdown")
summary_statistics <-
  list(
    "Statistics" =
      list(
        "Mean (sd)" = ~qwraps2::mean_sd(Returns, na_rm = TRUE),
        "median (Q1, Q3)" = ~qwraps2::median_iqr(Returns, na_rm = TRUE),
        "min" = ~min(Returns, na.rm = TRUE),
        "max" = ~max(Returns, na.rm = TRUE),
        "Cumulative Return"= ~sum(Returns, na.rm = TRUE)
      ),
    "Value At Risk" =
      list(
        "Normally Distributed VaR" = ~NDVaR(Returns),
        "Non-Normally Distributed VaR" = ~NON_NDVaR(Returns)
      )
  )

```




# BTC
```{r, echo = FALSE}
fig <- BTC %>% plot_ly(x = ~Date, type = "candlestick",
                      open = ~Open, close = ~Close,
                      high = ~High, low = ~Low) 
fig <- fig %>% layout(title = "BTC Chart", xaxis = list(rangeslider = list(visible = F)))
fig
```



## Table Of Statistics (Daily, Returns)

```{r, echo=FALSE}
kable(summary_table(BTC, summary_statistics))
```


## Plotting Returns (Daily, Returns)
```{r, echo=FALSE}
fig <- plot_ly(BTC, x = ~Date, y = ~Returns, type = 'scatter', mode = 'lines')
fig <- fig %>% layout(title = "BTC Chart")
fig
fig <- plot_ly(BTC, x = ~Returns, type = 'histogram')
fig
```




## Table Of Statistics (Daily, Log-Adjusted Returns)

```{r, echo = FALSE}

options(qwraps2_markup = "markdown")
LogSummary_Statistics <-
  list(
    "Statistics" =
      list(
        "Mean (sd)" = ~qwraps2::mean_sd(lReturns, na_rm = TRUE),
        "median (Q1, Q3)" = ~qwraps2::median_iqr(lReturns, na_rm = TRUE),
        "min" = ~min(lReturns, na.rm = TRUE),
        "max" = ~max(lReturns, na.rm = TRUE),
        "Cumulative Return"= ~sum(lReturns, na.rm = TRUE)
      ),
    "Value At Risk" =
      list(
        "Normally Distributed VaR" = ~NDVaR(lReturns),
        "Non-Normally Distributed VaR" = ~NON_NDVaR(lReturns)
      )
  )
kable(summary_table(BTC, LogSummary_Statistics))
```


## BTC With Historical Statistics Used to Deterministic Projection of Logarithmic Growth
```{r, echo = FALSE}
fig <- BTC %>% plot_ly(x = ~Date, type = "candlestick",
                      open = ~Open, close = ~Close,
                      high = ~High, low = ~Low) 
fig <- fig %>% add_lines(x = ~Date, y = LinearDeterministic, line = list(color = 'black', width = 0.75), inherit = T)
fig <- fig %>% layout(title = "BTC Chart", xaxis = list(rangeslider = list(visible = F)))
fig
```


## Simple Price Projection with Geometric Brownian Motion
```{r, echo = FALSE}
# Simulating Tesla Price Action Using Random Walk Theory
# Mu and sigma of the Stock or Asset
mu <- mean(BTC$Returns, na.rm = TRUE)
sig <- sd(BTC$Returns, na.rm = TRUE)
t <- nrow(BTC)
Starting_price <- BTC$Adj.Close[1]

# Start simulating prices
price <- rep(NA,t)
price[1] <- Starting_price
for(i in 2:t){
  price[i] <- price[i-1] + price[i-1]*(rnorm(1,mu,sig)/100)
}
Exp_Growth <- rep(NA, t)
Exp_Growth <- Starting_price
for(i in 2:t){
  Exp_Growth[i] <- Exp_Growth[i-1]*(mu/100)+Exp_Growth[i-1]
}

fig <- BTC %>% plot_ly(x = ~Date, type = "candlestick",
                      open = ~Open, close = ~Close,
                      high = ~High, low = ~Low) 
fig <- fig %>% add_lines(x = ~Date, y = LinearDeterministic, line = list(color = 'black', width = 0.75), inherit = T)
fig <- fig %>% add_lines(x = ~Date, y = price, line = list(color = 'purple', width = 0.75), inherit = T)
fig <- fig %>% layout(title = "BTC Chart", xaxis = list(rangeslider = list(visible = F)))
fig
```


## Multiple Price Projections with Geometric Brownian Motion
```{r, echo = FALSE}
# Simulating Tesla Price Action Using Random Walk Theory
# Mu and sigma of the Stock or Asset
mu <- mean(BTC$Returns, na.rm = TRUE)
sig <- sd(BTC$Returns, na.rm = TRUE)
t <- nrow(BTC)
Starting_price <- BTC$Adj.Close[1]

# Start simulating prices
price <- rep(NA,t)
price[1] <- Starting_price
for(i in 2:t){
  price[i] <- price[i-1] + price[i-1]*(rnorm(1,mu,sig)/100)
}


price1 <- rep(NA,t)
price1[1] <- Starting_price
for(i in 2:t){
  price1[i] <- price1[i-1] + price1[i-1]*(rnorm(1,mu,sig)/100)
}

price2 <- rep(NA,t)
price2[1] <- Starting_price
for(i in 2:t){
  price2[i] <- price2[i-1] + price2[i-1]*(rnorm(1,mu,sig)/100)
}


fig <- BTC %>% plot_ly(x = ~Date, type = "candlestick",
                      open = ~Open, close = ~Close,
                      high = ~High, low = ~Low) 
fig <- fig %>% add_lines(x = ~Date, y = LinearDeterministic, line = list(color = 'black', width = 0.75), inherit = T)
fig <- fig %>% add_lines(x = ~Date, y = price, line = list(color = 'purple', width = 0.75), inherit = T)
fig <- fig %>% add_lines(x = ~Date, y = price1, line = list(color = 'teal', width = 0.75), inherit = T)
fig <- fig %>% add_lines(x = ~Date, y = price2, line = list(color = 'blue', width = 0.75), inherit = T)
fig <- fig %>% layout(title = "BTC Chart", xaxis = list(rangeslider = list(visible = F)))
fig
```

## Subsetting the data Into 4 groups:
```{r}


```
